Comparison of Fast Imaging Architectures for Large, Multi-scale, Hierarchical Aperture Arrays

### 2024-06-13 ms.tex
Update on Overleaf.

The same reasoning can be extended for inter-station processing, where there is significant diversity. There is a large range in the number of stations and in the array filling factor. As a result, both the layout and cadence interval play significant roles in determining the efficiency of architectures.

>>>>

The same reasoning can be extended for inter-station processing, where there is significant diversity. There is a large range in the number of stations and in the array filling factor. As a result, both the layout and cadence interval play significant roles in determining the efficiency of architectures. For arrays with small numbers of stations such as \texttt{LAMBDA-I} and \texttt{CASPA}, the XBF architecture holds an advantage on all timescales. For arrays with large numbers of stations such as \texttt{SKA1-low-core} with a reasonably high packing density, EPIC holds the advantage on all timescales, but with slower cadence intervals, $t_\textrm{acc}\gtrsim 100$~ms, XBF and XFFT also have comparable efficiency. Although the \texttt{SKA1-low} has a large number of stations, they are not as densely packed as in the core, and therefore, the role of $t_\textrm{acc}$ is more significant. XFFT and EPIC are comparable at $t_\textrm{acc}\lesssim 1$~ms, but for $t_\textrm{acc}\gtrsim 100$~ms, XFFT is clearly advantageous. Similarly, \texttt{FarView} has a similar array filling factor as \texttt{SKA1-low-core}, but has far fewer stations. Hence, EPIC is only advantageous for $t_\textrm{acc}\lesssim 0.1$~ms, whereas XFFT becomes more efficient for $t_textrm{acc}\gtrsim 1$~ms.
